Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-03 mr-review.Rmd
added ukb ref

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
output: 
  - bookdown::html_document2
  - bookdown::word_document2
---

@@

Now, GWAS and Mendelian randomization for biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies, often greater than 100,000 subjects, offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller studies.

>>>>

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
output: 
  - bookdown::pdf_document2
  - bookdown::html_document2
  - bookdown::word_document2
---

@@

Modern GWAS for biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies, often greater than 100,000 
subjects, offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller studies. For example, the UK 
Biobank Study involves more than 500,000 subjects. Each UKB subject's 
data consists of millions of SNP genotypes and measurements for 
thousands of traits [@bycroft_uk_2018].
